Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
grammar edits

---
title: "Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness"
subtitle: "An Analysis of Potential Factors From 2000 to 2021"
author: 
  - Jenny Shen
  - Joyce Xuan
  - Jason Ngo
thanks: "Code and data are available at: https://github.com/jennyshen-playground/women_highest__level_education_20_years.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper utilizes data from the US General Social Survey to discuss women's level of education from 2000 to 2021. We find that the mean levels of education among surveyed women increased, as did their occupational prestige score and level of happiness. These findings matter as they enable us to understand the importance of women's access to higher education. The rise in occupational prestige scores can enhance economic development, and associates with increased levels of happiness. This suggests that advanced education leads to well-respected careers that generate happiness"
number-sections: true
bibliography: references.bib
---

@@

"The education of girls is the most powerful investment we can make in our collective future."

-Carrie Chapman Catt, Women's Suffrage Leader

@@

We will draw data from the US General Social Survey (henceforth GSS), which is available through the GSS website. Our respondents of interest are participants over 18 years of age who self-identify as women.

@@

In section 1, we discuss the source of data used in this paper, the strengths and weaknesses of GSS, methodologies that follow it, and data terminology. Section 2 discusses the results from our graphs, including the trend over the 20 year period. In section 3, we explore the factors that contribute to women's education levels and career prestige. In section 4, we provide an optional survey that we conducted to gather more information about women's educational attainment and career aspirations. The final section provides an analysis of the bias and ethical concerns, and weakness and steps.

@@

The data used in this paper is obtained from the US General Social Survey (henceforth GSS), and is available through the GSS website. Funded by the National Science Foundation and operated by the National Opinion Research Centre (NORC), the GSS has collected data regarding social change and growth complexity of American society since 1972. It keeps records of the practices, concerns, experiences, and attitudes of US residents. The survey randomly selects participants across the United States to take part in the survey. From those participants, only those that volunteer to participate are surveyed. Participants come from a mix of rural, urban and suburban areas. The survey is conducted face-to-face through an in-person interview conducted by staff at NORC. The survey itself takes around 90 minutes to complete. However, due to the pandemic, NORC had to change their collection methodology: the latest GSS was conducted through website and telephone interviews.

>>>>

---
title: "Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness"
subtitle: "An Analysis of Potential Factors From 2000 to 2021"
author: 
  - Jenny Shen
  - Joyce Xuan
  - Jason Ngo
thanks: "Code and data are available at: https://github.com/jennyshen-playground/women_highest__level_education_20_years.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper utilizes data from the US General Social Survey to discuss women's level of education from 2000 to 2021. We find that the mean levels of education among surveyed women increased, as did their occupational prestige score and level of happiness. These findings matter as they enable us to understand the importance of women's access to higher education. The rise in occupational prestige scores can enhance economic development, and also associates with increased levels of happiness. This suggests that advanced education leads to well-respected careers that generate happiness."
number-sections: true
bibliography: references.bib
---

@@

> "The education of girls is the most powerful investment we can make in our collective future."
>
> --- Carrie Chapman Catt, Women's Suffrage Leader

@@

We will draw data from the US General Social Survey (henceforth GSS), which is available through the GSS website [@citeGSS]. Our respondents of interest are participants over 18 years of age who self-identify as women.

@@

In section 1, we discuss the source of data used in this paper, the strengths and weaknesses of GSS, methodologies that follow it, and data terminology. Section 2 discusses the results from our graphs, including the trend over the 20 year period. In section 3, we explore the factors that contribute to women's education levels and career prestige. In section 4, we provide an optional survey that we conducted to gather more information about women's educational attainment and career aspirations. The final section provides an analysis of the bias and ethical concerns, as well as weaknesses and next steps.

@@

The data used in this paper is obtained from the US General Social Survey, and is available through the GSS website. Funded by the National Science Foundation and operated by the National Opinion Research Centre (NORC), the GSS has collected data regarding social change and growth complexity of American society since 1972. It keeps records of the practices, concerns, experiences, and attitudes of US residents. The survey randomly selects participants across the United States to take part in the survey. From those participants, only those that volunteer to participate are surveyed. Participants come from a mix of rural, urban and suburban areas. The survey is conducted face-to-face through an in-person interview conducted by staff at NORC. The survey itself takes around 90 minutes to complete. However, due to the pandemic, NORC had to change their collection methodology: the latest GSS was conducted through website and telephone interviews.
